Dependent Object Types

### 2012-08-30 doc/candidacy/report.tex
a bit more about tribe

In~\cite{tribe}, Clarke et al. present a calculus for virtual
classes. Virtual classes allow {\it families} of classes to be
inherited, rather than just single classes. Classes are lexically
nested inside other classes. When a class is inherited, its nested
inner classes are inherited along with its methods and fields. {\it
  Further binding} enables the nested classes to be further
extended. Path-dependent types arise naturally to distinguish objects
coming from different families. In Tribe, paths can additionally use
an ``out'' field to move from an object to the object which surrounds
it.

>>>>

In~\cite{tribe}, Clarke et al. present a calculus for virtual
classes. Virtual classes allow {\it families} of classes to be
inherited, rather than just single classes. Classes are lexically
nested inside other classes. When a class is inherited, its nested
inner classes are inherited along with its methods and fields. {\it
  Further binding} enables the nested classes to be further
extended. Path-dependent types arise naturally to distinguish objects
coming from different families. In Tribe, path types can depend
simultaneously on both classes and objects. Additionally, paths can
use an ``out'' field to move from an object to the object which
surrounds it. This ``out'' feature enables ubiquitous access to an
object's family without the need to drag around family arguments.
